Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-10-13 Rotation paper/draft_working.tex
Clarified discussion on window functions

One sees that all four window functions are fairly localized around specific values of $k$, which to a good approximation are described by Eq. \eqref{eq:kbtau}. This suggests that both equivalent- and near-equivalent-baseline delay-spectrum estimators are good estimators of the power spectrum. At higher $\ell$, the window functions for both estimators become elongated in $k$, with stronger tails towards the low $k$ modes where foregrounds reside. This is the phenomenology of the wedge, where at fine angular scales the foreground leakage to higher $k$ modes are more pronounced. Importantly, however, we note that the window functions for the near-equivalent-baseline estimator are no more elongated than for the equivalent-baseline estimator. One may thus conclude that the our proposed near-equivalent-baseline estimator does not result in extra foreground contamination of the EoR window.

>>>>

One sees that all four window functions are fairly localized around specific values of $k$, which to a good approximation are described by Eq. \eqref{eq:kbtau}. This suggests that both equivalent- and near-equivalent-baseline delay-spectrum estimators are good estimators of the power spectrum. \textbf{For window functions that are centered on higher $\ell$ modes, the window functions for both estimators become elongated in $k$, with stronger tails towards the low $k$ modes. Since the low $k$ modes are where the foregrounds reside, measurements of the high $\ell$ modes therefore mix in more foreground power.} This is the phenomenology of the wedge, where at fine angular scales the foreground leakage to higher $k$ modes are more pronounced. Importantly, however, we note that the window functions for the near-equivalent-baseline estimator are no more elongated than for the equivalent-baseline estimator. One may thus conclude that our proposed near-equivalent-baseline estimator does not result in extra foreground contamination of the EoR window.
